---
title: "279-keywords"
format: html
editor: visual
---
```{r}
library(rvest)
library(httr)
library(dplyr)
library(SnowballC)
library(tm) 
library(stringr)
```

### Step1: Get all pmid. 
1. create a function to get mid information from each website page. And then, we can create urls based on each unique pmid, and direct to each page, extract down the keywords. 

```{r}
get_pmid <- function(url) {
  page <- read_html(url)
  pmid <- page |>
    html_nodes('.docsum-pmid') |>
    html_text(trim = TRUE)
  return(data.frame(pmid = pmid))
}
```


2. create urls for all pages. 
```{r}
page_numbers <- 2:89
page_urls <- paste0("https://pubmed.ncbi.nlm.nih.gov/trending/?filter=simsearch1.fha&filter=years.2022-2024&page=", page_numbers)
```

3. create a whole dataframe for pmid 
```{r}
all_pmid <- list()
for (url in page_urls) {
  pmid_df <- tryCatch({
    get_pmid(url)
  }, error = function(e) {
    return(data.frame(pmid = character(0))) 
  })
  all_pmid[[url]] <- pmid_df
}
final_pmid_df <- bind_rows(all_pmid)
final_pmid_df 
```


4. now we get all the pmid, and we can create urls that direct to each passage page. 
```{r}
passage_urls <- paste0("https://pubmed.ncbi.nlm.nih.gov/", final_pmid_df$pmid, "/")
```


```{r}
get_keywords <- function(url) {
  page <- read_html(url)
  
  keyword_nodes <- page |>
    html_nodes(xpath = "//strong[contains(text(), 'Keywords:')]/parent::p")
  if (length(keyword_nodes) == 0) {
    return(NULL)
  } else {
    keyword_paragraph <- html_text(keyword_nodes, trim = TRUE)
    keyword_text <- sub("Keywords:\\s*", "", keyword_paragraph)
    keyword_text <- gsub("\\.$", "", keyword_text)
    keywords <- strsplit(keyword_text, ";\\s*")[[1]]
    return(data.frame(keywords = keywords))
  }
}
```


```{r}
all_keywords <- list()
for (url in passage_urls) {
  keywords_df <- tryCatch({
    get_keywords(url)
  }, error = function(e) {
    message(paste("Error in get_keywords for URL:", url, "Error:", e$message))
    return(data.frame(keywords = NA))
  })
  all_keywords[[url]] <- keywords_df
}
final_keywords_df <- bind_rows(all_keywords)
```


```{r}
final_keywords_df
```

```{r}
final_keywords_df$keywords <- tolower(final_keywords_df$keywords)

keyword_frequency <- final_keywords_df |>
  count(keywords, sort = TRUE) 
print(keyword_frequency)
```

Keywords Visualization 

```{r}
top_keywords <- head(keyword_frequency, 20)
```

```{r}
library(ggplot2)
ggplot(top_keywords, aes(x = reorder(keywords, n), y = n)) +
  geom_bar(stat = "identity") +
  xlab("Keywords") +
  ylab("Frequency") +
  coord_flip() +  # Flip the x and y axes for easier reading of labels
  theme_minimal() +
  ggtitle("Top 20 Keywords Distribution")

```



Data2: 
Google Scholar data: 
```{r}
base_url_template <- "https://scholar.google.com/scholar?start=%d&q=medicine&hl=en&as_sdt=0,34&as_ylo=2022&as_yhi=2024"

start_values <- seq(0, by = 10, length.out = 200)
url_list <- sprintf(base_url_template, start_values)
```


```{r}
get_highlighted_titles <- function(url) {
  page <- read_html(url)
  titles <- page |>
    html_nodes('h3.gs_rt a') |>
    html_text(trim = TRUE)
  return(titles)
}
```


```{r}
all_titles <- list()

for (url in url_list) {
  Sys.sleep(20)  # Add a delay because I encounter 429 error. 
  titles_vector <- tryCatch({
    get_highlighted_titles(url)
  }, error = function(e) {
    message(paste("Error in get_highlighted_titles for URL:", url, "Error:", e$message))
    return(character(0))
  })
  
  all_titles[[url]] <- data.frame(title = titles_vector)
}
final_titles_df <- bind_rows(all_titles)
print(final_titles_df)
```



```{r}
titles_df <- final_titles_df |>
  mutate(clean_title = tolower(title),
         clean_title = str_remove_all(clean_title, "[.,:]"))  
stop_words <- stopwords("en")
```


```{r}
# function to remove stop words. 
remove_stop_words <- function(string) {
  words <- str_split(string, "\\s+") |> unlist()
  words <- words[!words %in% stop_words]
  return(paste(words, collapse = " "))
}
```


```{r}
update_titles <- sapply(titles_df$clean_title, remove_stop_words)
titles_df$clean_title <- update_titles

word_list <- unlist(str_split(titles_df$clean_title, "\\s+"), use.names = FALSE)
word_df <- data.frame(word = word_list, stringsAsFactors = FALSE)
word_freq <- word_df |>
  group_by(word) |>
  summarise(count = n()) |>
  arrange(desc(count))
```

```{r}
print(word_freq)
```

```{r}
categories <- list(
  MedicineAndClinical = c("clinical", "surgery", "treatment", "therapy", "patient", "trial", "care", "vaccine", "transplantation", "pediatric", "nursing", "surgical", "pharmacology", "rehabilitation", "prognosis", "diagnosis", "anesthesia", "radiology","medicine"),
  HealthConditions = c("covid-19", "cancer", "diabetes", "infection", "alzheimer’s", "cardiovascular", "obesity", "depression", "hypertension", "arthritis", "diseases","pandemic","sars-cov-2"),
  BiomedicalScience = c("biotechnology", "genomics", "molecular", "cell", "biomarkers", "microbiome", "genetics", "neurology"),
  TechnologyInnovation = c("artificial intelligence", "machine learning", "data", "algorithm", "neural network", "imaging", "bioinformatics","precision","chatgpt","language","learning"),
  HealthSystemsPolicy = c("healthcare", "policy", "public health", "global health", "health system", "insurance", "medicaid", "medicare"),
  Other = c("other")  
)
```


```{r}
find_category_approx <- function(word, categories, max.distance = 0.3) {
  for (category_name in names(categories)) {
    if (any(agrep(word, categories[[category_name]], max.distance = max.distance, value = FALSE))) {
      return(category_name)
    }
  }
  return("Other") 
}
```


```{r}
find_category_vect = Vectorize(find_category_approx, vectorize.args = "word")

word_freq <- word_freq |>
  mutate(category = sapply(word, find_category_vect, categories = categories)) %>%
  group_by(category) %>%
  summarise(total_count = sum(count), .groups = 'drop') %>%
  arrange(desc(total_count))

print(word_freq)
```

